---
title: "harvesting"
author: "gparadis"
date: "05 April 2019"
output: pdf_document
---

# Overview

Provide an overview of what the module does / how to use the module.

Module documentation should be written so that others can use your module. This is a template for module documentation, and should be changed to reflect your module.

## R Markdown

R Markdown syntax allows R code, outputs, and figures to be rendered in the documentation.

For help writing in R Markdown, see <http://rmarkdown.rstudio.com/>.

# T

# Usage

```{r}
Sys.getenv()
```

```{r}
library(reticulate)
#Sys.unsetenv("RETICULATE_PYTHON")
#Sys.setenv("RETICULATE_PYTHON_ENV" = "r-reticulate")
#use_virtualenv("r-reticulate", required = TRUE)

```



# Events

Describe what happens for each event type.

## Plotting

Write what is plotted.

## Saving

Write what is saved.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module. If `sourceURL` is specified, `downloadData("harvesting", "path/to/modules/dir")` may be sufficient.

## Output data

Description of the module outputs.

# Links to other modules

Describe any anticipated linkages to other modules.
